<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{rgauges vignette}
-->

```{r, eval=TRUE, echo=FALSE}
opts_chunk$set(fig.width=6, fig.height=5, fig.pos="h")
```

rgauges vignette
=======

Gaug.es is a paid service for website analytics. It doesn't do as much as Google Analytics, but its super simple and clean, and has a great iPhone app, and an Android app. Each website you want to track is tracked under its own gauge. 

Most functions have the same format in which you pass in the id for a gauge (i.e, a website you are tracking), and your API key (see authentication below). Some functions give back data on your site overall and in that case you don't pass in a date, but others can be quieried per date or a range of dates, in which case you can pass in dates. There is one plotting function (`vis_gauge`) that gives a nice default plot. But of course you can easily make your own plots. 

## Gaug.es API docs

See the Gaug.es API documentation here [http://get.gaug.es/documentation/](http://get.gaug.es/documentation/)

`rgauges` is listed as one of the Gaug.es API libraries [here](http://get.gaug.es/documentation/api/libraries/), along with libraries for Ruby and Node.js

## Authentication

Get your own API key in your Gaug.es 'My Account' page and put in your _.Rprofile_ file under the name 'GaugesKey' or some other name (you can specify `keyname` in function calls - but if you put in as 'GaugesKey' you're all set and don't need to bother with the `keyname` parameter).

You can alternatively pass in your key using the `key` parameter in each function. 

Note that in the below examples I'm using my key from my _.Rprofile_ file, so you don't see it being passed in the function call. 


## Installation

More stable version from CRAN

```{r eval=FALSE}
install.packages("rgauges")
```

Development version from Github

```{r eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("rgauges", "ropensci")
```


```{r}
library(rgauges)
```

## Your info

Information on yourself.

```{r}
gs_me()
```

## Traffic

Traffic on a gauges ID

```{r}
gs_traffic(id='4efd83a6f5a1f5158a000004')
```


## Screen/browser information

Information on screen/browser resolutions

```{r}
gs_reso(id='4efd83a6f5a1f5158a000004')
```

## Visualize traffic data

You'll need to load ggplot2 

```{r}
library(ggplot2)
out <- gs_gauge_detail(id='4efd83a6f5a1f5158a000004')
vis_gauge(out)
```

## Shares

Lists the people that have access to a Gauge.

```{r}
gs_shares(id='4efd83a6f5a1f5158a000004')
```

## Referrers

Gets referrers for a gauge, paginated.

```{r}
gs_ref(id='4efd83a6f5a1f5158a000004', date = '2014-03-10')$data
```

## Technology

Gets browsers and platforms for a gauge.

```{r}
gs_tech(id='4efd83a6f5a1f5158a000004')
```

## Get pageviews for each page

```{r}
head( gs_pageviews(id='4efd83a6f5a1f5158a000004', fromdate="2013-11-01", todate="2013-11-06") )
```

## Top content

Gets top content for a gauge, paginated.

```{r}
head( gs_content(id='4efd83a6f5a1f5158a000004', date="2013-11-01")$data )
```

## Search terms

Gets search terms for a gauge, paginated.

```{r}
gs_terms(id='4efd83a6f5a1f5158a000004', date = '2014-02-05')$data
```

## Locations

Information on locations

```{r}
head( gs_locations(id='4efd83a6f5a1f5158a000004')$data )
```